\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}


% ----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Muhammad Haris Ahsan} \\ \vspace{1pt}
  \textbf{\small \scshape Software Engineer} \\ \vspace{5pt}
  % \small +92 327 600 0167 $|$
  \href{https://wa.me/+923276000167}{+92 327 600 0167}  $|$
  \href{mailto:harismirza3456@gmail.com}{harismirza3456@gmail.com}  $|$
  \href{https://www.linkedin.com/in/iamharisahsan/}{\underline{LinkedIn}} $|$
  \href{https://github.com/Haris-Mughal}{\underline{GitHub}} $|$
  \href{https://muhammad-haris-ahsan.vercel.app/}{\underline{Portfolio}} $|$
  \href{https://leetcode.com/u/Muhammad_Haris_Ahsan/}{\underline{LeetCode}}
\end{center}

%-----------1 - ACHIEVEMENTS-----------
\section{\textbf{Achievements}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape @GitHub:} {\href{https://github.com/Haris-Mughal/achievements/}{\underline{Achievements Repository}}}, contains approximately all my achievements of this journey.}
\resumeItem{\textcolor{blue}{\itshape @leetcode:} {\href{https://leetcode.com/u/Muhammad_Haris_Ahsan/}{\underline{Solved}}} 170+ Data Structures and Algorithms problems.[{\href{https://github.com/Haris-Mughal/leetcode-Solutions.py/}{\underline{Github link}}}]}
\resumeItem{\textcolor{blue}{\itshape @Lablab.ai:} {\href{https://lablab.ai/u/@muhammad_haris_ahsan569}{\underline{Participated}}} in AI International Hackathons}
\resumeItem{\textcolor{blue}{\itshape @Devpost:} {\href{https://devpost.com/iamharisahsan}{\underline{Participated}}} in International Hackathons}
\resumeItem{\textcolor{blue}{\itshape @Generative Ai:} {\href{https://community.genai.works/members/30362861}{\underline{Participated}}} in 'Build with Ai' International Ai Hackathon}
\resumeItem{\textcolor{blue}{\itshape @M{IT}²:} {\underline{Participated}} in 'Winter Contest' coding competition.}

\resumeItemListEnd

%-----------2 - Technical SKILLS-----------
\section{\textbf{Technical Skills}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape \textcolor{blue}{\itshape Programming Languages:}}{ JavaScript (ES6+), TypeScript, Python, C, C++} \\}
\resumeItem{\textcolor{blue}{\itshape Web Dev:}{ HTML5, CSS3, SCSS, SASS, Bootstrap 5, TailwindCSS 4, Shadcn UI, Ant Design, React JS(Context API, Router, State Management)} \\}
\resumeItem{\textcolor{blue}{\itshape Backend:}{ Firebase, Node JS, Express JS} \\}
\resumeItem{\textcolor{blue}{\itshape Version Control:}{ Git, Github} \\}
\resumeItem{\textcolor{blue}{\itshape Databases:}{ MongoDB, Firestore}\\}
\resumeItemListEnd
%

%-----------3 - EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{Government College University Faisalabad}{Dec 2022 - Present}
{CGPA: 2.87 / 4.00 - Till 3rd semester}{5th semester - ongoing}
{}{}
\resumeItemListStart
\resumeItem{Bachelor of Sciences in Computer Science}
\resumeItemListEnd

\resumeSubheading
{Punjab College Science, Faisalabad}{2020 - 2022}
% {CGPA: 2.87 / 4.00 - Till 3rd semester}{5th semester - ongoing}
{}{}
\resumeItemListStart
\resumeItem{FSC Pre-medical}

\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------6 - VOLUNTEER Experience-----------
\section{\textbf{Volunteer Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{Trainer and Moderator}{August 2024 -- Present}
{{\href{https://www.linkedin.com/company/icode-guru/mycompany/}{\underline{iCodeGuru}}}}{Santa Clara, California · Remote}
\resumeItemListStart
\resumeItem {Offered volunteer teaching in Python and DSA at iCodeGuru, emphasizing LeetCode.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%



%-----------7 - Hackathons & Competitions-----------
\section{\textbf{Hackathons and Competitions}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Advent of Code 2024}} $|$ [{\href{https://www.linkedin.com/posts/iamharisahsan_adventofcode-codingjourney-problemsolving-activity-7279979607758393344--OZK}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Completed all 25 days of Advent of Code 2024, tackling progressively challenging algorithmic puzzles.}
\resumeItem{Optimized solutions using dynamic programming, graph traversal, and bitwise operations.}
\resumeItem{Ranked among top global participants, demonstrating speed, efficiency, and problem-solving skills.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{LabLab AI - AI for Connectivity Hackathon}} $|$ [{\href{https://www.linkedin.com/posts/iamharisahsan_aiforconnectivity-5gplanning-innovation-activity-7289356432993349632-VMJP}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Competed in a global hackathon with a 5-member team from UAE, Rwanda, and Pakistan.}
\resumeItem{Developed an AI-powered solution to enhance real-time digital connectivity.}
\resumeItem{Integrated machine learning models for optimized data transmission and accessibility.}
\resumeItem{Presented a working prototype to judges, emphasizing scalability and real-world impact.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{GenAI - BuildWithAI Hackathon}} $|$ [{\href{https://www.linkedin.com/posts/iamharisahsan_project-presentation-activity-7294032973849362432-tWb7}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Collaborated in a team of 8 participants, including 4 mentors from the US, New Zealand, Switzerland, Germany, and Pakistan.}
\resumeItem{Developed an AI-powered chatbot using Generative AI technologies to provide efficient solutions.}
\resumeItem{Integrated cutting-edge AI models and collaborated with mentors to refine project ideas.}
\resumeItem{Showcased the chatbot’s capabilities, emphasizing real-world applications and scalability.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{Devpost - XR Design Hackathon}} $|$ [{\href{https://www.linkedin.com/posts/iamharisahsan_xr-design-challenge-project-presentation-activity-7284840549180710913-MceO}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Collaborated in a team of 6 with participants from the US and Pakistan to create an immersive XR experience.}
\resumeItem{Developed a React website, a Flutter mobile app, and a GenAI app as part of the project.}
\resumeItem{Integrated cutting-edge technologies to create an interactive, cross-platform experience.}
\resumeItem{Showcased a functional prototype, demonstrating the potential of XR in real-world applications.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{MM\{IT\}² Winter Contest 2025}} $|$ [{\href{https://www.linkedin.com/posts/iamharisahsan_mit2wintercontest-codingcompetition-icodeguru-activity-7286864579068882944-mUuH}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Competed in a global coding contest with a team of 3 participants, all from Pakistan.}
\resumeItem{Secured 94th place worldwide out of thousands of participants, showcasing strong problem-solving skills.}
\resumeItem{Collaborated to solve algorithmic challenges and optimized solutions under time constraints.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%

%-----------8 - PERSONAL PROJECTS-----------
\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{{CosmoLearn}} $|$ \emph{HTML, CSS, JavaScript, React, TailwindCSS, Python, Flutter, GenAI, XR, AR, VR, Hugging Face}}
{}

\resumeItemListStart
\resumeItem{Developed an XR, AR, and VR educational platform for exploring the solar system.}
\resumeItem{Created interactive 3D solar system experiences to simplify complex astronomical concepts, enhancing student engagement.}
\resumeItem{Built a multi-platform solution with a web app (React, TailwindCSS) and mobile app (Flutter), integrated with GenAI for enhanced learning.}
\resumeItem{Led development, ensuring seamless compatibility across platforms and delivering a live demo for global audiences.}
\resumeItemListEnd
\resumeItemListStart
\resumeItem{\textbf{Project on Devpost:} \href{https://devpost.com/software/cosmolearn}{\underline{Devpost link}}}
\resumeItem{\textbf{Live Demo:} \href{https://xr-universe.vercel.app/}{\underline{Web Demo}}}
\resumeItem{\textbf{Web UI GitHub Repository:} \href{https://github.com/Haris-Mughal/XR-Universe-WebUI}{\underline{GitHub link}}}
\resumeItem{\textbf{Mobile App GitHub Repository:} \href{https://github.com/Haris-Mughal/XR-Universe-MobApp}{\underline{GitHub link}}}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{Smart Network Planning}} $|$ \emph{Machine Learning, Vector Search, Large Language Models (LLMs), Milvus, Streamlit, AI, Data Science}}{}
\resumeItemListStart
\resumeItem{Developed a 5G deployment solution leveraging ML, LLMs, and vector search for optimized network planning and improved connectivity.}
\resumeItem{Implemented AI-driven resource allocation and traffic balancing, optimizing 5G network deployment to reduce inefficiencies.}
\resumeItem{Automated complex tasks like network analysis and site selection, saving time and reducing errors in 5G planning.}
\resumeItem{Designed scalable architecture using Milvus for efficient processing of large datasets, ensuring seamless performance.}
\resumeItemListEnd
\resumeItemListStart
\resumeItem{\textbf{Project on lablab.ai:} \href{https://lablab.ai/event/ai-for-connectivity-hackathon/the-techies/5g-intelligent-allocation-tool}{\underline{lablab.ai link}}}
\resumeItem{\textbf{Live Demo:} \href{https://rajeshthangaraj1-smart-network-planning.hf.space/}{\underline{live link}} (login:'admin', pass:'admin@123')}
\resumeItem{\textbf{GitHub Repository:} \href{https://github.com/Haris-Mughal/Ai-Connectivity-Hackathon}{\underline{GitHub link}}}
\resumeItemListEnd


\resumeProjectHeading
{\textbf{{AURAFem}} $|$ \emph{Python, Streamlit, NLP, Machine Learning, AI, Chatbot Development} $|$ [{\href{https://github.com/Haris-Mughal/AURAFem-chatbot}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Developed a FemTech web app for ovarian cancer with personalized AI-powered health support.}
\resumeItem{Created a conversational AI-agent using NLP for human-like responses and machine learning for continuous improvement.}
\resumeItem{Implemented emotional intelligence to enhance user interactions with empathetic responses.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}